A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-01 graph_syntax.tex
staring work on a monday morning

\subsection{Obtaining the Fundamental Problem Formulation Graph}
In general, there may be multiple different graphs that satisfy the FPG conditions, though there may be none at all. Here, we describe a process for obtaining an FPG by starting with the MCG and disconnecting explicit edges until the FPG conditions are met. Then the problem is reduced to deciding which explicit edges to remove.

>>>>

\subsection{Obtaining the Fundamental Problem Graph}
In general, there may be multiple different graphs that satisfy the FPG conditions, though there may be none at all. Here, we describe a process for obtaining an FPG by starting with the MCG and disconnecting explicit edges until the FPG conditions are met. Then the problem is reduced to deciding which explicit edges to remove.
